### 2024-06-02 player-evaluation.qmd
20240602 - so-called intangibles

Other factors to consider include cognitive and motivational factors
Cognitive and motivational factors one could consider include:

>>>>

Other factors to consider include cognitive and motivational factors.
Some coaches refer to these as the "X Factor" or "the intangibles."
However, just as any other construct in psychology, we can devise ways to operationalize them.

Cognitive and motivational factors one could consider include:
